## Task 2. Exploraring a dataset

For this task you have to use dataset from file `airquality.csv`. The description of the data you can find by the [link](https://www.rdocumentation.org/packages/datasets/versions/3.6.2/topics/airquality).

Example, how to work with the dataset. For instanse, we want to find month (column `Month`) with highest mean temperature (`Temp`)


```{r message=FALSE}
library(dplyr)

airquality |> 
  group_by(Month) |> 
  summarise(mean_temp = mean(Temp)) |> 
  filter(mean_temp == max(mean_temp))
```

You task is to answer the following questions about this data by writing appropriate code.

1. What are the column names of the data frame?

```{r}
names(airquality)
```

2. What are the row names of the data frame?

```{r}
row.names(airquality)
```


3. Extract the first 6 rows of the data frame and print them to the console
```{r}
head(airquality)
```

4. How many observations (i.e. rows) are in this data frame?
```{r}
nrow(airquality)
```

5. Extract the last 6 rows of the data frame and print them to the console
```{r}
tail(airquality)
```

6. How many missing values are in the "Ozone" column of this data frame?

```{r}
sum(is.na(airquality$Ozone))
```

7. What is the mean of the "Ozone" column in this dataset? Exclude missing values (coded as NA) from this calculation.

```{r}
mean(airquality$Ozone, na.rm = TRUE)
```


8. Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90.

```{r}
#with(airquality, subset(Ozone > 31, Temp > 90))
#subset(airquality, Ozone > 31 & Temp > 90)
airquality %>% 
  filter(Ozone > 31, Temp > 90)
```



```{r}
require(graphics)
pairs(airquality, panel = panel.smooth, main = "airquality data")
```


