
## Task 4. Functions

```{r}
library(dplyr)
```


Create the next functions and test them with a few different arguments:

1. Function `above(x, n)` which returns all items of vector `x` that more than `n`. By default `n = 10`. For instance, `above(c(3, 5, 6), 5)` returns `6`.

```{r}
above <- function(x, n=10) {
  x[x > n]
}
```


2. Function `my_ifelse(x, exp, n)` which compares all items of vector `x` with `n` using expression `exp`. `exp` can be `<`, `<=`, `>`, `=>`, `==`. For instance, `exp(c(3, 5, 6), "=>", 5)` returns `5, 6`.

```{r}
my_ifelse <- function(x, exp, n=20) {
  if (exp == "<") { 
    res <- x[x < n]
  } else if (exp == "<=") {
    res <- x[x <= n]
  } else if (exp == ">") {
    res <- x[x > n]
  } else if (exp == ">="){
    res <- x[x >= n]
  }else if (exp == "=="){
    res <- x[x == n]
  }else {
    res <- x
  }
  
  res
}
my_ifelse(10:30, "<", 20)
my_ifelse(10:30, "<=", 20)
my_ifelse(10:30, ">", 20)
my_ifelse(10:30, ">=", 20)
my_ifelse(10:30, "==", 20)
```


3. Function `my_columnmean(df, removeNA)` that returns mean value for each column of data frame or matrix `df`. Logical argument `removeNA` set whether remove NA values or not. By default `removeNA = True`. Use loop `for` of `while` for the function.

```{r}
my_columnmean <- function(df, removeNA){
    apply(df, 2, mean, na.rm = removeNA)
}

my_columnmean(airquality, removeNA = TRUE)
```


